---
title: Simulations for Simultaneous Goodness-of-fit Testing
header-includes: \usepackage{color}
                 \usepackage{float}
output:
  html_document: default
  pdf_document:
    fig_caption: no
---


```{r, echo=FALSE}
if(!("simdata" %in% dir()))
  dir.create("simdata")
nolibraries <- FALSE
tmp <- try(library(simgof), silent=TRUE)
if(substring(tmp[1], 1, 5)=="Error") {
  cat("Install library simgof from CRAN\n")
  nolibraries <- TRUE
} else {library(simgof)}
library(knitr)
library(gridExtra)
library(cowplot)
opts_chunk$set(echo=FALSE,
               message=FALSE,
               warning=FALSE,
               error=TRUE)
```

```{r}
if(nolibraries) {
  knitr::exit()
}
```

**WARNING: knitting the full Rmd will take several hours!!**

## General Setup

```{r}
B <- 10000 # Number of simulation runs for null distribution
Bpower <- 10000 # Number of simulation runs for power
all.methods <- c("KS", "AD", "CdM", "W",   "ZK", "ZA", "ZC", "ppcc", "RGd")
normal.methods <- c(all.methods, "SW", "JB", "sNor")
uniform.methods <- c(all.methods, "sUnif")
exponential.methods <- c(all.methods, "sExp")
chisquare.methods <- c("RGd", "Equal Size", "Equal Prob")
custom.shape <-   c(20, 1:16-1)
```


## R routines

-  **Routine for drawing power curves**

```{r}
do.graph <- function(out, xlbl) {
  Methods <- colnames(out)
  xvals=case$alt.param=as.numeric(rownames(out))
  mns <- apply(out, 2, mean)
  ordr <- order(mns, decreasing = TRUE)
  cs <- custom.shape[ordr]
  m <- length(case$alt.param)
  df <- data.frame(
      x=rep(xvals, length(Methods)),
      Power=c(out),
      Method=factor(rep(Methods, each=m),
        levels=Methods[ordr],
        ordered=TRUE)
  )
df1 <- df[df$Method=="RC", ]
plt <- ggplot(data=df, aes(x, Power , shape=Method)) +
  geom_point() +
  xlab(xlbl) +
  geom_line(data=df1, aes(x, Power)) +
  scale_shape_manual(values=cs)
 print(plt)

}
```

-  **Routine for finding power of tests**

```{r}
simgof.power <- function(case, alpha=0.05) {
# Find distributions of test statistics under the null hypothesis
  m <- length(case$methods)
  znull <- matrix(0, case$B, length(case$methods))
  colnames(znull) <- case$methods
  param <- case$param
  for(i in 1:case$B) {
    case$n <- ifelse(is.null(case$lambda), case$n, rpois(1, case$lambda))
    x <- case$rnull(case$n, param)
    if(!is.null(case$param)) case$param <- case$est.mle(x)
    znull[i, ] <- simgof::TS(x, case)
  } 
# Find p value distributions  
  tmp <- rep(0, length(case$methods))
  names(tmp) <- case$methods
  pval <- rep(0, case$B)
  for(i in 1:case$B) {
    xsim <- znull[sample(1:case$B, 1), ]
    for(k in case$methods) 
      tmp[k] <- sum(xsim[k]<znull[, k])/case$B      
    pval[i] <- min(tmp)
  } 
  
# Find cdf of p values
  x <- seq(0, 1, length=250)
  y <- 0*x
  for(i in 1:250) y[i] <- sum(pval<=x[i])/length(pval)
  xy <- cbind(x, y)
  adjust <- function(xy, a) {
    approx(x=xy[, 1], y=xy[, 2], xout=a, rule=2)$y
  } 
# Find power(s)   
  tmp <- matrix(0, length(case$alt.param), length(case$methods)+1)
  colnames(tmp) <- c("RC", case$methods)
  rownames(tmp) <- case$alt.param
  reject <- as.list(seq_along(alpha))
  for(k in seq_along(alpha))
    reject[[k]] <- tmp
    pvals <- rep(0, length(case$methods)+1)
    names(pvals) <- c("RC", case$methods)
    for(j in seq_along(case$alt.param)) {
      ralt <- function(n)
        case$ralt(n, case$alt.param[j])
      for(i in 1:case$Bpower) {
        case$n <- ifelse(is.null(case$lambda), case$n, rpois(1, case$lambda))
        x <- ralt(case$n)
        if(!is.null(case$param)) case$param <- case$est.mle(x)
        tmp <- simgof::TS(x, case)
        for(k in case$methods) {
          pvals[k] <- sum(tmp[k]<znull[, k])/case$B
        }
        pvals["RC"] <- adjust(xy, min(pvals[-1]))
        for(k in seq_along(alpha))
          reject[[k]][j, ] <- reject[[k]][j, ] +
              ifelse(pvals<alpha[k], 1, 0)
      }
  }
  for(k in seq_along(alpha))
      reject[[k]] <- round(100*reject[[k]]/case$Bpower, 1)
  if(length(alpha)==1) return(reject[[1]])
  reject
}
```


-  **Routine for finding power using parallel processing**

```{r}
simgof.power.parallel <- function(case) {
   num_cores <- parallel::detectCores()-1
   if(num_cores==1) return(simgof.power(case))
   cl <- parallel::makeCluster(num_cores)
   z <- parallel::clusterCall(cl, simgof.power, case)
   out <- 0*z[[1]]
   for(i in 1:num_cores)
      out <- out+z[[i]]
   parallel::stopCluster(cl)
   round(out/num_cores, 1)
}
```

## Bonferroni Solution

```{r}
case <- list(
  B = B,
  Bpower  = Bpower,
  param = NULL,
  n = 1000,
  pnull = function(x, param) pnorm(x),
  rnull = function(n, p=c(0, 1)) rnorm(n),
  qnull = function(p, param) qnorm(p),
  qnull = function(p, param=NULL) qnorm(p),
  LR = c(-Inf, Inf),
  alt.param = 1,
  methods = normal.methods,
  est.mle = function(x) NA
)
```

```{r}
bonferroni <- function(case,
                  alpha=c(0.01, 0.05, 0.1)) {
  alpha <- alpha/length(case$methods)
  znull <- matrix(0, case$B, length(case$methods))
  colnames(znull) <- case$methods
  for(i in 1:case$B) {
    x <- case$rnull(case$n)
    znull[i, ] <- simgof::TS(x, case)
  }
  reject <- rep(0, length(alpha))
  for(i in 1:case$Bpower) {
    x <- case$rnull(case$n)
    tmp <- simgof::TS(x, case)
    pvals <- tmp
    for(m in case$methods)
      pvals[m] <- sum(tmp[m]<znull[, m])
    pvals <- pvals/case$B
    for(k in seq_along(alpha))
      if(any(pvals<alpha[k]))
        reject[k] <- reject[k] + 1
  }
  round(100*reject/case$Bpower, 1)
}
```

- Bonferroni

```{r bonf, cache=TRUE}
tn <- 1
bonferroni(case)
```


## ANOVA example

```{r anova, cache=TRUE}
t <- 1
k <- 5
pvals <- rep(0, B)
for(i in 1:B) {
  x <- rnorm(100)
  y <- sample(1:k, 100, replace = TRUE)
  tmp <- NULL
  for(j in 1:(k-1)) {
    for(m in (j+1):k)
      tmp <- c(tmp, t.test(x[y==j], x[y==m])$p.value)
  }
  pvals[i] <- min(tmp)
}
x <- seq(0, 1, length=250)
y <- x
for(i in 1:250) y[i] <- sum(pvals<x[i])/B
tpvals <- approx(x, y, pvals)$y
df <- data.frame(pvals, tpvals)
c(sum(tpvals<0.01), sum(tpvals<0.05), sum(tpvals<0.1))/B
df1 <- data.frame(x=rep(x, 3), 
  y=c(y, y2=1-(1-x)^10, y3=x),
  which=rep(c("ECDF", "Indep.", "No adjust."), each=250)
)
```


```{r}
bw <- 1/50 
plt1 <- ggplot(df, aes(pvals)) +
  geom_histogram(aes(y = ..density..),
    color = "black", 
    fill = "white", 
    binwidth = bw) +
    labs(x="p value", y="")
plt2 <- ggplot(data=df1, aes(x, y, group=which)) +
  geom_line(aes(linetype=which)) +
  scale_linetype_manual(values=c("solid", "dotted", "twodash")) +
  labs(x="p", y="") +
  theme(legend.title = element_blank())
plt3 <- ggplot(df, aes(tpvals)) +
  geom_histogram(aes(y = ..density..),
    color = "black", 
    fill = "white", 
    binwidth = bw) +
    labs(x="Transformed p value", y="")
```  

```{r}
plt5 <- plot_grid(plt1, plt2, plt3, nrow=2)
plt5
#save_plot("figANOVA.pdf", plt5)
```

## Null distributions

-  N(0,1)

```{r}
case <- list(
  B = B,
  Bpower = Bpower,
  param = NULL,
  n = 1000,
  pnull = function(x, param) pnorm(x),
  rnull = function(n, p=NULL) rnorm(n),
  qnull = function(p, param) qnorm(p),
  ralt = function(n, p=NULL) rnorm(n),
  LR = c(-Inf, Inf),
  alt.param = 1,
  methods = normal.methods,
  est.mle = function(x) NA
)
```


```{r case01, cache=TRUE}
tn <- 2
out <- NULL
n <- c(100, 500, 1000)
for(i in n) {
  case$n <- i
  z <- simgof.power(case, alpha=c(0.01, 0.05, 0.1))
  out <- rbind(out,
      c(z[[1]][1], z[[2]][1], z[[3]][1]))
}
colnames(out) <- c("1%", "5%", "10%")
rownames(out) <-
  paste0("N(0,1),n=", c(100, 500, 1000))
```

- Normal, mean and sd estimated

```{r case02, cache=TRUE}
tn <- 2
case$param = c(0, 1)
case$pnull = function(x, param)
    pnorm(x, param[1], param[2])
case$qnull = function(x, param=c(0,1))
    qnorm(x, param[1], param[2])
case$rnull = function(n, param=c(0,1))
    rnorm(n, param[1], param[2])
case$ralt = function(n, param=c(0,1)) rnorm(n)
case$est.mle = function(x) c(mean(x), sd(x))
n <- c(100, 500, 1000)
for(i in n) {
  case$n <- i
  z <- simgof.power(case, alpha=c(0.01, 0.05, 0.1))
  out <- rbind(out,
      c(z[[1]][1], z[[2]][1], z[[3]][1]))
}
rownames(out)[nrow(out)-2:0] <-
  paste0("N,n=", c(100, 500, 1000))
```

```{r}
n.out <- out
```


- U[0,1]

```{r}
case$methods <- uniform.methods
out <- NULL
```


```{r case03, cache=TRUE}
tn <- 2
out <- NULL
case$param = NULL
case$pnull = function(x, param) punif(x)
case$rnull = function(n, p=NULL) runif(n)
case$ralt = case$rnull
case$qnull = function(p, param) qunif(p)
case$LR = c(0, 1)
case$est.mle = function(x) NULL
n <- c(100, 500, 1000)
for(i in n) {
  case$n <- i
  z <- simgof.power(case, alpha=c(0.01, 0.05, 0.1))
  out <- rbind(out,
      c(z[[1]][1], z[[2]][1], z[[3]][1]))
}
rownames(out)[nrow(out)-2:0] <-
  paste0("U[0,1],n=", c(100, 500, 1000))
```

```{r}
u.out <- out
```

- Exponential(1)

```{r}
case$methods <- exponential.methods
out <- NULL
```


```{r case04, cache=TRUE}
tn <- 1
case$param = NULL
case$pnull = function(x, param) pexp(x, 1)
case$rnull = function(n, p=1) rexp(n, 1)
case$ralt = case$rnull
case$qnull = function(p, param) qexp(p, 1)
case$LR = c(0, Inf)
case$est.mle = function(x) NULL
n <- c(100, 500, 1000)
for(i in n) {
  case$n <- i
  z <- simgof.power(case, alpha=c(0.01, 0.05, 0.1))
  out <- rbind(out,
      c(z[[1]][1], z[[2]][1], z[[3]][1]))
}
rownames(out)[nrow(out)-2:0] <-
  paste0("Exp(1),n=", c(100, 500, 1000))
```

- Exponential, rate estimated

```{r case05, cache=TRUE}
tn <- 1
case$param = 1
case$pnull = function(x, param)
  pexp(x, param)
case$rnull = function(n, p=1) rexp(n, p)
case$ralt = case$rnull
case$qnull = function(p, param=1) qexp(p, param)
case$LR = c(0, Inf)
case$est.mle = function(x) 1/mean(x)
n <- c(100, 500, 1000)
for(i in n) {
  case$n <- i
  z <- simgof.power(case, alpha=c(0.01, 0.05, 0.1))
  out <- rbind(out,
      c(z[[1]][1], z[[2]][1], z[[3]][1]))
}
rownames(out)[nrow(out)-2:0] <-
  paste0("Exp,n=", c(100, 500, 1000))
```

```{r}
case$methods <- all.methods
```

- Beta(3, 1/2)

```{r case06, cache=TRUE}
tn <- 2
case$param = NULL
case$pnull = function(x, param)
  pbeta(x, 3, 1/2)
case$rnull = function(n, p=NULL) rbeta(n, 3, 1/2)
case$ralt = case$rnull
case$qnull = function(p, param) qbeta(p, 3, 1/2)
case$LR = c(0, 1)
case$est.mle = function(x) NULL
n <- c(100, 500, 1000)
for(i in n) {
  case$n <- i
  z <- simgof.power(case, alpha=c(0.01, 0.05, 0.1))
  out <- rbind(out,
      c(z[[1]][1], z[[2]][1], z[[3]][1]))
}
rownames(out)[nrow(out)-2:0] <-
  paste0("Beta(3, 0.5),n=", c(100, 500, 1000))
```

- Gamma(3, 2)

```{r case07, cache=TRUE}
tn <- 2
case$param = NULL
case$pnull = function(x, param) pgamma(x, 3, 2)
case$rnull = function(n, p=NULL) rgamma(n, 3, 2)
case$ralt = case$rnull
case$qnull = function(p, param) qgamma(p, 3, 2)
case$LR = c(0, Inf)
case$est.mle = function(x) NULL
n <- c(100, 500, 1000)
for(i in n) {
  case$n <- i
  z <- simgof.power(case, alpha=c(0.01, 0.05, 0.1))
  out <- rbind(out,
      c(z[[1]][1], z[[2]][1], z[[3]][1]))
}
rownames(out)[nrow(out)-2:0] <-
  paste0("Gamma(3, 2),n=", c(100, 500, 1000))
```


```{r}
out <- rbind(n.out, u.out,  out)
colnames(out) <- c("1%", "5%", "10%")
df <- data.frame(
  Distribution=c(rep("Normal", 6), rep("Uniform", 3),
                 rep("Exponential", 6), rep("Beta", 3),
                 rep("Gamma", 3)),
  Parameter=c(rep("Fixed", 3), rep("Estimated", 3),
              rep("Fixed", 6), rep("Estimated", 3),
              rep("Fixed", 6)
              ),
  SampleSize = rep(c(100, 500, 1000), each=7),
  out)
colnames(df)[4:6] <- c("1%", "5%", "10%")
df
saveRDS(df, "simdata/nulltable.rds")
df
```

## Power

### Case 0, Normal vs t(df)

```{r}
case <- list(
  methods = normal.methods,
  param = c(0, 1),
  B = B,
  Bpower  = Bpower,
  n = 1000,
  pnull = function(x, param=c(0,1))
    pnorm(x, param[1], param[2]),
  rnull = function(n, p=c(0, 1))
    rnorm(n, p[1], p[2]),
  qnull = function(p, param=c(0,1))
    qnorm(p, param[1], param[2]),
  alt.param = 3*1:20,
  ralt = function(n, p=c(0,1)) rt(n, p),
  est.mle = function(x) c(mean(x), sd(x)),
  LR = c(-Inf, Inf)
)
```


```{r case0, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```

```{r}
saveRDS(list(out=out, varname="Degrees of Freedom"), "simdata/case0.rds")
do.graph(out, "Degrees of Freedom")
all.normal.cases <- out
```


### Case 1: Normal(0,1) vs t(df)

```{r}
case <- list(
  methods = normal.methods,
  param = NULL,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param) pnorm(x),
  rnull = function(n, p=c(0, 1)) rnorm(n),
  qnull = function(p, param) qnorm(p),
  alt.param = 3*1:20,
  ralt = function(n, p) rt(n, p),
  est.mle = function(x) NULL,
  LR = c(-Inf, Inf)
)
```

```{r case1, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="Degrees of Freedom"), "simdata/case1.rds")
do.graph(out, "Degrees of Freedom")
all.normal.cases <- rbind(all.normal.cases, out)
```

### Case 2, Normal vs Beta(q, q)

```{r}
case <- list(
  methods = normal.methods,
  param = c(0.5, 0.1),
  B = B,
  Bpower  = Bpower,
  n = 1000,
  pnull = function(x, param=c(0.5, 0.1))
    pnorm(x, param[1], param[2]),
  rnull = function(n, p=c(0.5, 0.1))
    rnorm(n, p[1], p[2]),
  qnull = function(p, param=c(0.5, 0.1))
    qnorm(p, param[1], param[2]),
  alt.param = 4:23,
  ralt = function(n, q=1) rbeta(n, q, q),
  est.mle = function(x) c(mean(x), sd(x)),
  LR = c(-Inf, Inf)
)
```


```{r case2, cache=TRUE}
tn <- 2
out <- simgof.power.parallel(case)
```

```{r}
saveRDS(list(out=out, varname="q"), "simdata/case2.rds")
do.graph(out, "q")
all.normal.cases <- rbind(all.normal.cases, out)
```


### Case 3: Normal(r, $\sqrt{r}$) vs Gamma(r, 1)

```{r}
case <- list(
  methods = normal.methods,
  param = NULL,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  qnull=0,
  est.mle = function(x) NULL,
  LR = c(-Inf, Inf)
)
```


```{r case3, cache=TRUE}
tn <- 1
out <- matrix(0, 20, length(case$methods)+1)
r <- 10*1:20
rownames(out) <- paste("r =", r)
colnames(out) <- c("RC", case$methods)
for(i in 1:20) {
  case$alt.param <- r[i]
  case$pnull <- function(x, param)
    pnorm(x, r[i], sqrt(r[i]))
  case$qnull <- function(p, param) qnorm(p, r[i], sqrt(r[i]))
  case$rnull <- function(n, p=1) rnorm(n, r[i], sqrt(r[i]))
  case$ralt <- function(n, r) rgamma(n, r, 1)
  out[i, ] <- simgof.power(case)
}
```


```{r}
rownames(out) <- 10*1:20
case$alt.param <- 10*1:20
saveRDS(list(out=out, varname="r"), "simdata/case3.rds")
do.graph(out, "r")
all.normal.cases <- rbind(all.normal.cases, out)
```

### Case 4: Normal vs Gamma(r, 1)

```{r}
case <- list(
  param = 0,
  methods = normal.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  qnull=0,
  alt.param = 1,
  est.mle = function(x) mean(x),
  LR = c(-Inf, Inf)
)
```


```{r case4, cache=TRUE}
tn <- 2
out <- matrix(0, 20, length(case$methods)+1)
rownames(out) <- paste("r =", r)
colnames(out) <- c("RC", case$methods)
r <-  10*1:20
for(i in 1:20) {
  case$param <- r[i]
  case$pnull <-  function(x, param=r[i])
    pnorm(x, param, sqrt(param))
  case$qnull <- function(p, param=r[i])
    qnorm(p, param, sqrt(param))
  case$rnull <- function(n, p=r[i])
    rnorm(n, p, sqrt(p))
  case$ralt <- function(n, p)
    rgamma(n, r[i], 1)
  out[i, ] <- simgof.power(case)
}
```



```{r}
rownames(out) <- r
case$alt.param <- r
saveRDS(list(out=out, varname="r"), "simdata/case4.rds")
do.graph(out, "r")
all.normal.cases <- rbind(all.normal.cases, out)
```

## Performance with H~0~: Normal

```{r PerformanceNormal}
round(sort(apply(all.normal.cases, 2, mean)), 1)
```

### Case 5: Uniform[0,1] vs Linear

```{r}
case <- list(
  param = NULL,
  methods = uniform.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param)  punif(x),
  rnull = function(n, p=1) runif(n),
  qnull = function(p, param) qunif(p),
  alt.param = round(seq(0, 0.3, length=20), 2),
  ralt = function(n, slope) {
    if (slope == 0)
        return(runif(n))
    (slope - 1 + sqrt((1 - slope)^2 +
              4 * slope * runif(n)))/2/slope
  },
  est.mle = function(x) NULL,
  LR = c(0, 1)
)
```


```{r case5, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```

```{r}
saveRDS(list(out=out, varname="Slope"), "simdata/case5.rds")
do.graph(out, "Slope")
all.uniform.cases <- out
```


### Case 6: Uniform[0,1] vs Beta(1, q)

```{r}
case <- list(
  param = NULL,
  methods = uniform.methods,
  est.mle = function(x) NULL,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param)  punif(x),
  rnull = function(n, p=1) runif(n),
  qnull = function(p, param) qunif(p),
  alt.param = sort(c(1, seq(0.8, 1.2, length=19))),
  ralt = function(n, p) rbeta(n, 1, p),
  LR = c(0, 1)
)
```


```{r case6, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="q"), "simdata/case6.rds")
do.graph(out, "q")
all.uniform.cases <- rbind(all.uniform.cases, out)
```


### Case 7: Uniform[0,1] vs Beta(q, q)

```{r}
case <- list(
  param = NULL,
  methods = uniform.methods,
  est.mle = function(x) NULL,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param)  punif(x),
  rnull = function(n, p=1) runif(n),
  qnull = function(p, param) qunif(p),
  alt.param = sort(c(1, seq(0.8, 1.2, length=19))),
  ralt = function(n, p) rbeta(n, p, p),
  LR = c(0, 1)
)
```



```{r case7, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="q"), "simdata/case7.rds")
do.graph(out, "q")
all.uniform.cases <- rbind(all.uniform.cases, out)
```

### Case 8: Uniform[0,1] vs Quadratic


```{r}
case <- list(
  param = NULL,
  methods = uniform.methods,
  est.mle = function(x) NULL,
  B = 1000,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param)  punif(x),
  rnull = function(n, p=1) runif(n),
  qnull = function(p, param) qunif(p),
  alt.param = round(sort(c(0, seq(-1, 1, length=19))), 2),
  ralt = function(n, a)  {
    dquad <- function(x) 3*a*(x-0.5)^2+1-a/4
    if(a==0) return(runif(n))
    cc <- ifelse(a>0, dquad(0), dquad(0.5))
    y <- rep(0, n)
    for(i in 1:n) {
      repeat {
        u <- runif(1)
        if(runif(1)<dquad(u)/cc) {y[i]<-u;break}
      }
    }
    y
  },
  LR = c(0, 1)
)
```



```{r case8, cache=TRUE}
tn <- 2
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="a"), "simdata/case8.rds")
do.graph(out, "a")
all.uniform.cases <- rbind(all.uniform.cases, out)
```


## Performance with H~0~: Uniform

```{r PerformanceUniform}
round(sort(apply(all.uniform.cases, 2, mean)), 1)
```



### Case 9: Exponential  vs Exponential(1)+Normal(1.5, sigma)


```{r}
case <- list(
  param = 1,
  methods = exponential.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  dnull = function(x, param) dexp(x, param),
  pnull = function(x, param) pexp(x, param),
  rnull = function(n, p=1) rexp(n, 1),
  qnull = function(p, param) qexp(p, 1),
  alt.param = round(seq(1, 0.3, length=20), 2),
  ralt = function(n, p) {
    z <- sample(0:1, n, replace = TRUE, prob=c(9, 1))
    y <- rnorm(10*n, 1.5, p)
    y <- y[y>0][1:n]
    ifelse(z==0, rexp(n, 1), y)
  },
  est.mle = function(x) 1/mean(x),
  LR = c(0, Inf)
)
```

```{r case9, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="sd"), "simdata/case9.rds")
do.graph(out, "sd")
all.expo.cases <- out
```

### Case 10: Exponential(1) vs Gamma(p, 1)

```{r}
case <- list(
  param = NULL,
  methods = exponential.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param=1) pexp(x, 1),
  rnull = function(n,p=1) rexp(n, 1),
  qnull = function(p, param=1) qexp(p, 1),
  alt.param = sort(c(1, seq(0.8, 1.2, length=19))),
  ralt = function(n, p) rgamma(n, p, 1),
  est.mle = function(x) NULL,
  LR = c(0, Inf)
)
```



```{r case10, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="p"), "simdata/case10.rds")
do.graph(out, "p")
all.expo.cases <- rbind(all.expo.cases, out)
```


### Case 11: Exponential vs Gamma(p, 1)

```{r}
case <- list(
  param = 1,
  methods = exponential.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param=1) pexp(x, param),
  rnull = function(n,p=1) rexp(n, p),
  qnull = function(p, param=1) qexp(p, param),
  alt.param = sort(c(1, seq(0.8, 1.2, length=19))),
  ralt = function(n, p) rgamma(n, p, 1),
  est.mle = function(x) 1/mean(x),
  LR = c(0, Inf)
)
```



```{r case11, cache=TRUE}
tn <-1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="p"), "simdata/case11.rds")
do.graph(out, "p")
all.expo.cases <- rbind(all.expo.cases, out)
```

### Case 12: Exponential vs Inverse Power

```{r}
case <- list(
  param = 1,
  methods = exponential.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param=1) pexp(x, param),
  rnull = function(n,p=1) rexp(n, p),
  qnull = function(p, param=1) qexp(p, param),
  alt.param = round(seq(5, 30, length=20), 1),
  ralt = function(n, p) {
    y=runif(2*n)^(-1/(p-1))-1
    y[y<10][1:n]
  },
  est.mle = function(x) 1/mean(x),
  LR = c(0, Inf)
)
```


```{r case12, cache=TRUE}
tn <- 2
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="a"), "simdata/case12.rds")
saveRDS(out, "simdata/case13.rds")
do.graph(out, "a")
all.expo.cases <- rbind(all.expo.cases, out)
```



## Performance with H~0~: Exponential

```{r PerformanceExponential}
round(sort(apply(all.expo.cases, 2, mean)), 1)
```


### Case 13: Truncated Exponential(0.5, 0, 1) vs Linear(p)

```{r}
case <- list(
  param = NULL,
  methods = all.methods,
  est.mle = function(x) NULL,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param=0.5) {
    y <- (1 - exp(-0.5*x))/(1 - exp(-0.5))
    y[y<0] <- 0;y[y>1]<-1
    y
  },
  rnull = function(n, p=0.5) {
    x <- NULL
    repeat {
        x <- c(x, rexp(n, 0.5))
        x <- x[x < 1]
        if (length(x) > n)
            break
    }
    x[1:n]
  },
  qnull = function(p, param=0.5)
    -log(1 - p*(1 - exp(-0.5)))/0.5,
  alt.param = seq(-0.25, -0.55, length=20),
  ralt = function(n, slope) {
    if (slope == 0)
        return(runif(n))
    (slope - 1 + sqrt((1 - slope)^2 +
                        4 * slope * runif(n)))/2/slope
  },
  LR = c(0, 1)
)
```

```{r case13, cache=TRUE}
tn <- 2
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="Slope"), "simdata/case13.rds")
do.graph(out, "Slope")
all.cases <-  out
```



### Case 14: Truncated Exponential(., 0, 1) vs Linear(p)

```{r}
case <- list(
  param = 0.5,
  methods = all.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param=0.5) {
    y <- (1 - exp(-0.5*x))/(1 - exp(-0.5))
    y[y<0] <- 0;y[y>1]<-1
    y
  },
  rnull = function(n, p=0.5) {
    x <- NULL
    repeat {
        x <- c(x, rexp(n, p))
        x <- x[x < 1]
        if (length(x) > n)
            break
    }
    x[1:n]
  },
  qnull = function(p, param=0.5)
    -log(1 - p*(1 - exp(-param)))/param,
  alt.param = seq(-0.2, -0.95, length=20),
  ralt = function(n, slope) {
    if (slope == 0)
        return(runif(n))
    (slope - 1 + sqrt((1 - slope)^2 +
                        4 * slope * runif(n)))/2/slope
  },
  est.mle = function (x, A = 0, B = 1)
  {
    n <- length(x)
    s <- sum(x)
    p <- n/s
    repeat {
        o <- p
        tmp1 <- exp(-o * A) - exp(-o * B)
        tmp2 <- B * exp(-o * B) - A * exp(-o * A)
        tmp3 <- A^2 * exp(-o * A) - B^2 * exp(-o * B)
        l1 <- n/o - s - n * tmp2/tmp1
        l2 <- (-n/o^2 - n * (tmp3 * tmp1 - tmp2^2)/tmp1^2)
        p <- o - l1/l2
        if (abs(p - o) < 0.001)
            break
    }
    p
  },
  LR = c(0, 1)
)
```

```{r case14, cache=TRUE}
tn <- 2
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="Slope"), "simdata/case14.rds")
do.graph(out, "Slope")
all.cases <- rbind(all.cases, out)
```


### Case 15: Beta(2, 2), vs Beta(2, 2, p)


```{r}
case <- list(
  param = NULL,
  methods = all.methods,
  est.mle = function(x) NULL,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size,
  pnull = function(x, param)
    pbeta(x, 2, 2),
  rnull = function(n, p=c(2, 2))
    rbeta(n, 2, 2),
  qnull = function(p, param)
     qbeta(p, 2, 2),
  alt.param = seq(0, 0.75, length=20),
  ralt = function(n, p) rbeta(n, 2, 2, ncp=p),
  est.mle = function(x) NULL,
  LR = c(0, 1)
)
```



```{r case15, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="ncp"), "simdata/case15.rds")
do.graph(out, "ncp")
all.cases <- rbind(all.cases, out)
```

### Case 16: Beta(1, .), vs Linear(a)


```{r}
case <- list(
  param = 1,
  methods = all.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size,
  pnull = function(x, param=1)
    pbeta(x, 1, param),
  rnull = function(n, p=1)
    rbeta(n, 1, p),
  qnull = function(p, param=1)
     qbeta(p, 1, param),
  alt.param = seq(0, -0.7, length=20),
  ralt = function (n, slope) {
    if (slope == 0)
        return(runif(n))
    (slope - 1 + sqrt((1 - slope)^2 +
                4 * slope * runif(n)))/2/slope
  },
  est.mle = function(x) -1/mean(log(1-x)),
  LR = c(0, 1)
)
```


```{r case16, cache=TRUE}
tn <- 2
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="Slope"), "simdata/case16.rds")
do.graph(out, "Slope")
all.cases <- rbind(all.cases, out)
```

### Case 17: Erlang(.,.) vs Gamma($\alpha, 5$)

uses a non-mle estimator for k and $\lambda$.

```{r}
est.mm <- function(x, p=case$param) {
  c(round(mean(x)^2/var(x)), mean(x)/var(x))
}
```


```{r}
case <- list(
  param = c(2, 5),
  methods = all.methods,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size,
  pnull = function(x, param)
    pgamma(x, 2, 5),
  rnull = function(n, p=c(2, 5))
    rgamma(n, 2, 5),
  qnull = function(p, param)
     qgamma(p, 2, 5),
  alt.param = seq(1.75, 2.25, length=20),
  ralt = function(n, p) rgamma(n, p, 5),
  est.mle = est.mm,
  LR = c(0, Inf)
)
```


```{r case17, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="alpha"), "simdata/case17.rds")
do.graph(out, "alpha")
all.cases <- rbind(all.cases, out)
```

### Case 18: Uniform[0,1] vs Beta(1, q), binned data


```{r}
case <- list(
  param = NULL,
  methods = uniform.methods,
  est.mle = function(x) NULL,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param) punif(x),
  rnull = function(n, p=1) runif(n),
  qnull = function(p, param) qunif(p),
  alt.param = sort(c(1, seq(0.8, 1.2, length=19))),
  ralt = function(n, p) {
    bins=seq(0,1,length=51)
    mid=(bins[-1]+bins[-51])/2
    p=diff(pbeta(bins, 1, p))
    x=sample(mid, size=n, replace = TRUE, prob = p)
    list(bins=bins,
         counts=hist(x, bins, plot=FALSE)$counts)
  },
  LR = c(0, 1)
)
```

```{r case18, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="q"), "simdata/case18.rds")
do.graph(out, "q")
```

### Case 19: Normal vs t(n), binned data


```{r}
case <- list(
  methods = normal.methods,
  param = c(0, 1),
  B = B,
  Bpower  = Bpower,
  n = 1000,
  pnull = function(x, param=c(0,1))
    pnorm(x, param[1], param[2]),
  rnull = function(n, p=c(0, 1))
    rnorm(n, p[1], p[2]),
  qnull = function(p, param=c(0,1))
    qnorm(p, param[1], param[2]),
  alt.param = 3*1:20,
  ralt = function(n, p) {
    bins= seq(-3, 3, length=51)
    mid=(bins[-1]+bins[-51])/2
    pb=c(pt(bins[2], p),
        diff(pt(bins[2:50], p)),
        1-pt(bins[50], p))
    x=sample(mid, size=n, replace = TRUE, prob = pb)
    list(bins=bins,
         counts=hist(x, bins, plot=FALSE)$counts)
  },
  est.mle = function(x) c(mean(x), sd(x)),
  LR = c(-Inf, Inf)
)
```


```{r case19, cache=TRUE}
tn <- 1
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="Degrees of Freedom"), "simdata/case19.rds")
do.graph(out, "Degrees of Freedom")
```

### Case 20: Uniform[0,1] vs Beta(1, q), Poisson sample size


```{r}
case <- list(
  param = NULL,
  methods = uniform.methods,
  est.mle = function(x) NULL,
  B = B,
  Bpower  = Bpower,
  n = 1000, # sample size
  pnull = function(x, param) punif(x),
  rnull = function(n, p=1) runif(n),
  qnull = function(p, param) qunif(p),
  alt.param = sort(c(1, seq(0.8, 1.2, length=19))),
  ralt = function(n, p) rbeta(n, 1, p),
  lambda = 1000,
  LR = c(0, 1)
)
```

```{r case20, cache=TRUE}
tn <- 2
out <- simgof.power.parallel(case)
```


```{r}
saveRDS(list(out=out, varname="q"), "simdata/case20.rds")
do.graph(out, "q")
```

### Create Tables and Graphs

```{r}
for(i in 0:0) {
  out <- readRDS(paste0("../simdata/case", i, ".rds"))[[1]]
  mt <- apply(out, 2, mean)
  m <- colnames(out)[order(mt, decreasing = TRUE)]
  cat("Case ", i, "\n", 
      paste0(m[1:(length(m)-2)],", "), 
      m[length(m)-1], " and ", m[length(m)], ".\n")
}
```


1. **Power Curves**

```{r eval=FALSE}
for(i in 0:20) {
  print(paste("Case", i))
  out <- readRDS(paste0("../simdata/case", i, ".rds"))
  print(do.graph(out))
  ggsave(paste0("figCase", i, ".pdf"))
}  
```


2. **Results**

```{r}
mt <- c("RC", all.methods)
out <- NULL
for(i in 0:17) {
  tmp <- readRDS(paste0("../simdata/case",i,".rds"))[[1]]
  out <- rbind(out, tmp[, mt])
}  
all.cases <- out
all.cases <- as.matrix(all.cases)
cat("Mean Power Overall\n")
mn <- apply(all.cases, 2, mean)
round(sort(mn, decreasing = TRUE), 2)
cat("Mean Power and  Ranks by case\n")
rnks <- matrix(0, 18, 10)
mns <- matrix(0, 18, 10)
for(i in 0:17) {
  tmp <- readRDS(paste0("../simdata/case", i, ".rds"))[[1]][, mt]
  tmp1 <- apply(tmp, 2, mean)
  mns[i+1, ] <- tmp1
  rnks[i+1, ] <- round(rank(tmp1))
}
colnames(mns) <- mt
colnames(rnks) <- mt
mt <- colnames(all.cases)[order(mn, decreasing = TRUE)]
mns <- mns[, mt]
rnks <- rnks[, mt]
rownames(rnks)=paste("Case",1:18)
rnks1 = 10-rnks
kable.nice(rnks1)
cat("Mean Ranks\n")
round(sort(apply(rnks1, 2, mean)),1)
tmp <- matrix(0, 10, 10)
colnames(tmp) <- colnames(rnks)
row.names(tmp) <- 1:10
bins=seq(0.5, 10.5, 1)
for(i in 1:10) { 
  tmp[, i]  <- hist(rnks[, i], bins, plot=FALSE)$counts
} 
df1 <- data.frame(Case=rep(1:18, 10),
  Means=c(mns),
  Methods=rep(factor(mt, 
              levels=mt,ordered=TRUE), each=18))
df2 <- data.frame(Method=rep(1:10, each=10),
                 Ranks=rep(10:1, 10),
                 counts=c(tmp))
df2$counts[df2$counts==0]=-1
cat("Graph of Mean Power by Case\n")
ggplot(data=df1, aes(Case, Means, color=Methods)) +
  geom_point()  +
  scale_x_continuous(breaks=1:21)
cat("Graph of Ranks\n")
ggplot(data=df2, aes(Method, Ranks)) +
  geom_point(size=df2$counts) +
  scale_x_continuous(breaks=1:10,labels = colnames(rnks)) +
  scale_y_continuous(breaks=1:10) +
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
#ggsave("figResult1.pdf")
```

```{r}
out <- matrix(0, 18, 10)
colnames(out) <- c("RC", all.methods)
rownames(out) <- 0:17
for(i in 1:18) {
  tmp <- readRDS(paste0("../simdata/case",i-1,".rds"))[[1]]
  z <- apply(tmp, 1, max)
  if(max(z)<90) next
  tmp <- tmp[z>90, ,drop=FALSE]
  z <- z[z>90]
  if(nrow(tmp)>1) tmp <- tmp[order(z), ][1, 1:10]
  else {tmp <- c(tmp)[1:10]}
  out[i, ] <- tmp
}
out <- out[out[,1]>0,]
mt <- apply(out, 2, mean)
df2 <- data.frame(Method=rep(1:10, each=nrow(out)),
                 Power=c(out))
cat("Power of methods if best method has power of about 80%\n")
ggplot(data=df2, aes(Method, Power)) +
  geom_point() +
  scale_x_continuous(breaks=1:10,labels = colnames(out))
ggsave("figResult2.pdf")
```

